\chapter{Future Work}
\label{ch:futurework_report}

The future work ideas discussed here. \\ \\

With given scope and time limits of present thesis work, we have picked up important among the research questions formed while brainstorming on the thesis topic theme. So, here are some list of research questions that we consider for future work. \\ \\

In the scope of the first primary research question, i.e., display of results, here are few more sub research questions. So far we have looked into the ideas of having a list either single combining all results or separate for each tool and also having tags with tool names for each bug finding in an analysis view. As with separate lists idea being the user need to scroll to see different tool results, it will be interesting to know if having tabs help in scalability of bug findings since it would overcome the scrolling issue. \\ \\

During the first UX design cycle, we have seen the importance of having a statistics screen. So, on that aspect, we could test whether or not graphs help the target users. If so, will users need separate graphs for each tool or in combination? Again, in case of a single graph, should it be with combined results by default or users need filters for it. \\ \\

\begin{enumerate}
\item Would having tabs help scale the tools visibility with bugs results?
\item Do graphs help in understanding the bugs reported?
\item Will the user need to have graphs for separate tools or one graph combining the tools selected?
\item In scenarios of having unique (single) graph for multiple tools, does user expect to have it shown all the tools integrated by default or need of filters for tools selection? \\ \\
\end{enumerate} 

In the scope of the third primary research question, i.e., traceability of bug fixing here is one more sub research question.  During UX 2 and UX 3 design cycles, we have looked into aspect of having multiple windows and a table view for tracking the changes in a particular section of code. We found out the designs being novel; the users are challenged to understand at first glance in few seconds. So, we have an idea about showing graphs like histogram which might help to comprehend easily at first glance. \\ \\
\noindent Does having graphs (example: histograms) at particular part of code with commits related bug fixes help the user to trace? \\ \\

Until now, we focused on scenarios with sub research questions from a single developer perspective in doing tasks such as finding a bug and fixing it by himself. As the users tend to work in teams for more significant projects, we also consider to add new main research question looking into aspect of teamwork in fixing bugs. \\ \\
\noindent RQ 4 - How is teamwork facilitated in bug fixing in context of multiple tools? \\ \\

Also, it would be interesting to evaluate the complete prototype by covering the sub research questions into a single prototype. As we have promising finalised solution ideas through evaluation for each different scenarios in using multiple tools with a single interface, we look forward to develop a real interface when feasible technology stack and resources available. \\ \\

As mentioned in Chapter \ref{ch:limitations_report} about the design tool, it would be good to consider if there is an alternative tool that could help with animation features. It makes it more easier to understand than the present approach.